Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-14 Journal1/Response (21-10-2019)/Response.tex

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem. The results seem promising but the paper has some issues. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text. A proofread is required before it can be accepted for publication.   ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I have changed the paper's introduction and checked the text entirely according to this comment.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment 2:} ``Although the paper demonstrates its claims, the relaxation of conditions from the original problem formulation is not well justified. It is not clear why the initial formulation of the problem is not feasible and the reformulated makes it feasible while retaining some level of quality of the solutions given. A deeper analysis of both formulations must be presented. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
The problem (13) is feasible and has feasibility points that are discussed in subsection  IV-B, and we introduce a fast algorithm (algorithm 3) for feasibility points. Although the problem is feasible, it is not convex and difficult to solve.. Since problem (13) is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard. Solving the problem is complex. To solve the problem by inspiring Stackelberg, we reformulate the equation (13g) to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader). So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation (15) because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.

We also add this response in subsection III-A.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``Moreover, the baseline and FBDR methods used in the comparison are not well introduced. They are vaguely linked to related work but not as needed. The paper must clarify the relation of the related work and the compared alternatives. The paper must also contextualize the proposal among the related work by comparing their qualities and/or performance.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
 Two different methods are used to compare with the performance of the proposed method (IABV) and show the optimality of our approach. The first one is a baseline scheme, which uses random PRB allocation. So, the allocation of PRB to each UE is random when we have low interference, but in figures with high interference, we randomly assign just one RB to each UE. Also, the association of O-RU is carried out based on distance. It means that each UE is assigned to the nearest O-RU. The optimal power is obtained using the CVX of Matlab, which uses the successive convex approximation (SCA) method since the problem is convex. 
After achieving power and other parameters, the achievable rate will be obtained and the optimal number of VNF is
achieved from the lemma (1). The second one is similar
to the fixed BBU capacity and dynamic resource allocation
(FBDR) algorithm proposed in [18]. In this work, we have services with different QoS that
contain UEs, which is similar to tenants with different QoS
that is introduced in [18]. So, we used an algorithm similar
to FBDR adapted to our conditions for comparison. Instead
of BBU in C-RAN, we have O-DU and O-CU in O-RAN.
To use the FBDR method, we should consider the fixed
BBU capacity. We assume that O-DU and O-CU have fixed
sufficient capacity in our system model. Also, our mid-haul
link (F1 link) has adequate capacity, so there will be no
issue using the FBDR method by separating BBU to O-DU
and O-CU with this assumption. In this method, PRB and power are dynamically allocated. The number of VNFs is
obtained from the simulation. The UEs are associated with the O-RU based on the quality of their channels and the
channel distance instead of using the greedy algorithm 1 (GAA algorithm ) for O-RU assignment. The figures in [18]
show that dynamic BBU capacity and dynamic resource allocation (DBDR) perform better than FBDR for the same
priority area. We will also see that our proposed algorithm performs better than FBDR in the numerical result section.

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment4:} ``Finally, the source of the values used for the parameters in the evaluation must be clarified.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We refer to the following list of references in our numerical result for this comment:

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{green!10}
[1] 3GPP-TS-36.104-V13.3.0, “Evolved Universal Terrestrial Radio Access (E-UTRA);
Base Station (BS) radio transmission and reception
(Release 13),” 2016-03.

[2]  3GPP-TR-36.931-V13.0.0, “Technical Specification Group Radio Access Network;
Evolved Universal Terrestrial Radio Access (E-UTRA);
Radio Frequency (RF) requirements for LTE Pico Node B
(Release 13),” 2016-01.

[3] 3GPP-TS-25.101-V4.13.0, “User equipment (UE) radio transmission
and reception (FDD)(release 4),” 2006-12.

[4]E. Mohyeldin, “Minimum technical performance requirements for
imt-2020 radio interface(s),” 2020.

[5]  ETSI-TR-138-913-V14.3.0, “5G; study on scenarios and require-
ments for next generation access technologies(3GPP TR 38.913 version
14.3.0 release 14),” 2017-10.

\\
\hline
\end{longtable}

In [1] page 11, the amount of BW is explained. In [2], noise power is represented. In [5], the author stated the amount of delay for eMBB and URLLC in page 24 and 25. Also, in page 27, the mMTC packet size is stated. In [3], in page 13, table 6.1, the maximum power is stated. In [4], in page 4, the delay of URLLC and eMBB is stated also the spectral efficiency of eMBB is stated.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!45}
\textbf{Reviewer 2} \\
\hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author:} ``The paper focus on the aspect of network slicing in 5G cellular network which entails a service aware resource allocation of the different required virtual network functions (VNFs) for different slices which have different characteristics. More specifically, the paper proposes a mixed integer mathematical problem which in the original form is non-linear and hence hard to solve. To tackle this challenge the optimization problem is decomposed into two sub-problems where the solutions are not optimal however numerical investigations show that the solutions are competitive. In general, the paper is well written and structured.''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for careful and thorough reading of this manuscript and
for the thoughtful comments and constructive suggestions, which help us to improve the quality of
this manuscript. We hope that the responses provided herein can alleviate the reviewer concerns.

### 2022-02-14 Journal1/paper3TNSM/pr.tex
add reviewer 1 comments

\textcolor{violet}{Although the problem is feasible and it has feasibility points that are discussed in subsection \ref{fr}, it is not convex and difficult to solve. Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard. Solving the problem is complex. To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader). So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation \eqref{lb1} because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}

@@

and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a}.

@@

\textcolor{brown}{ The second one is similar to the fixed BBU capacity and
dynamic resource allocation (FBDR) algorithm proposed in \cite{lee2018dynamic}.
In this work, we have services with different QoS that contain UEs, which is similar to tenants with a different QoS. So, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
 We assume here that the capacity of the O-DU (which is similar to BBU in the FBDR) is as large as the capacity of our fronthaul link so that we can use this method for our system model.

>>>>

\textcolor{violet}{The problem \ref{problem} is feasible and has feasibility points that are discussed in subsection \ref{fr}, and we introduce a fast algorithm (algorithm\ref{alg3}) for feasibility points. Although the problem is feasible, it is not convex and difficult to solve. Since problem \eqref{problem} is mixed-integer nonlinear programming with two integer constraints which are a binary variable ($e$ shows the PRB assignment) and an integer variable ($M_s$ indicate the number of VNFs in slice s), the problem is NP-hard. Solving the problem is complex. To solve the problem by inspiring Stackelberg, we reformulate the equation \eqref{c16} to reduce one of the variables ($M_s$) that can be solved after obtaining the rate of UEs ($M_s$ is similar to followers in Stackelberg Competition and power and PRB assignment is similar to leader). So, the new problem has two variables of power and PRB assignment. This new problem is convex by relaxing the binary variable (PRB assignment) and estimating the lower bounds in equation \eqref{lb1} because the objective function and constraints of the problem are convex and can be solved by the Lagrangian function. After obtaining the power of UEs and PRB assignment, we can obtain the achievable rate of each UE so we can find the optimal number of VNFs.}

@@

and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$. The other parameters of these simulations are depicted in Table \ref{table:1a} \cite{3GPPTS1, 3GPPTS2, 3GPPTS3, IMT, ETSI1}.

@@

\textcolor{brown}{ In this work, we have services with different QoS that contain UEs, which is similar to tenants with different QoS that is introduced in \cite{lee2018dynamic}.
 So, we used an algorithm similar to FBDR adapted to our conditions for comparison.  
Instead of BBU in C-RAN, we have O-DU and O-CU in O-RAN. To use the FBDR method, we should consider the fixed BBU capacity. We assume that O-DU and O-CU have fixed sufficient capacity in our system model. Also, our mid-haul link (F1 link) has adequate capacity, so there will be no issue using the FBDR method by separating ‌BBU to O-DU and O-CU with this assumption.
